Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support).

### 2017-02-08 csf-2017/paper.tex
a bit of text about the FTLR

\subsection{Fundamental theorem of logical relations}

\begin{theorem}[Fundamental Theorem]
  \label{thm:ftlr}
  For all $n$, $\perm$, $\start$, $\addrend$, $\addr$, $\gl$, $W$, if one of the following holds:
  \begin{align*}
      & \bullet
        \begin{aligned}[t]
        &\perm = \exec \text{\footnotesize{ and }}\\
        &\npair{(\start,\addrend)} \in \readCond{}(\gl)(W)
      \end{aligned} \\
    & \bullet 
      \begin{aligned}[t]
        &\perm = \rwx \text{\footnotesize{ and }} \\
        &\npair{(\start,\addrend)} \in \readCond{}(\gl)(W) \text{\footnotesize{ and }}\\
        &\npair{(\start,\addrend)} \in \writeCond{}(\iota^\nwl,\gl)(W)
      \end{aligned} \\
    & \bullet 
      \begin{aligned}[t]
        &\perm = \rwlx \text{\footnotesize{ and }}\\
        &\npair{(\start,\addrend)} \in \readCond{}(\gl)(W) \text{\footnotesize{ and }}\\
        &\npair{(\start,\addrend)} \in \writeCond{}(\iota^\pwl,\gl)(W),
      \end{aligned}
  \end{align*}
  then
  \[
    \npair{((\perm,\gl),\start,\addrend,\addr)} \in \stder(W)
  \]
\end{theorem}

>>>>

With the logical relation defined, we can now state a strong theorem
about the safety properties of the capability machine. Namely that any
capability that does not grant unreasonable authority is capability
safe as a program counter.

\begin{theorem}[Fundamental Theorem]
  \label{thm:ftlr}
  For all $n$, $\perm$, $\start$, $\addrend$, $\addr$, $\gl$, $W$, if one of the following holds:
  \begin{align*}
      & \bullet
        \begin{aligned}[t]
        &\perm = \exec \text{\footnotesize{ and }}\\
        &\npair{(\start,\addrend)} \in \readCond{}(\gl)(W)
      \end{aligned} \\
    & \bullet 
      \begin{aligned}[t]
        &\perm = \rwx \text{\footnotesize{ and }} \\
        &\npair{(\start,\addrend)} \in \readCond{}(\gl)(W) \text{\footnotesize{ and }}\\
        &\npair{(\start,\addrend)} \in \writeCond{}(\iota^\nwl,\gl)(W)
      \end{aligned} \\
    & \bullet 
      \begin{aligned}[t]
        &\perm = \rwlx \text{\footnotesize{ and }}\\
        &\npair{(\start,\addrend)} \in \readCond{}(\gl)(W) \text{\footnotesize{ and }}\\
        &\npair{(\start,\addrend)} \in \writeCond{}(\iota^\pwl,\gl)(W),
      \end{aligned}
  \end{align*}
  then
  \[
    \npair{((\perm,\gl),\start,\addrend,\addr)} \in \stder(W)
  \]
\end{theorem}
When proving correctness of properties of programs, the Fundamental
Theorem serves as a way to reason about the execution of unknown
programs. For instance if the capability for a program only grants access to
instructions and data, then the capability is capability safe as a
program counter. The theorem also serves as a sanity check of the
logical relation as it makes sure that a large class of capabilities
actually inhabits it.
